Object-Oriented Internet\\ Cloud Interoperability

### 2021-03-23 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Review ICCS 2021 notification for paper 136 #60
- Review 1 - improved abstract

      Optimization of industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely Industry 4.0 and Industrial Internet of Things. The research aims at working out a new generic architecture and deployment scenario applicable to that integration. The reactive interoperability relationship of the interconnected nodes is proposed to deal with the network traffic propagation asymmetry or assets' mobility. The described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment. The discussion addressing generic architecture concludes that the embedded gateway software part best suits all requirements. To promote separation of concerns and reusability, the proposed architecture of the embedded gateway has been implemented as a composable part of the selected OPC UA PubSub framework.

      The proposals are backed by proof of concept reference implementations confirming the possibility to integrate selected cloud services with the cyber-physical system interconnected as one whole atop of the OPC UA by applying the proposed architecture and deployment scenario. It is contrary to interconnecting cloud services with the selected OPC UA server limiting the PubSub role to data export only.

>>>>

      Optimization of industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely the fourth industrial revolution coined as Industry 4.0 and Industrial Internet of Things. The following research aims at working out a new generic architecture and deployment scenario applicable to that integration. A~reactive interoperability relationship of the communication parties is proposed to deal with the network traffic propagation asymmetry or assets’ mobility. Described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment. The discussion  concludes that the embedded gateway software component best suits all requirements and thus has been implemented as a composable part of the selected reactive OPC UA framework which promotes separation of concerns and reusability.

      The proposals are backed by proof-of-concept reference implementations confirming the possibility of integrating selected cloud services with the OPC UA based cyber-physical system by applying the proposed architecture and deployment scenario. It is contrary to interconnecting cloud services with the selected OPC UA Server limiting the PubSub role to data export only.
